InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-06 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

\section{Conclusion}

>>>>

\section{Conclusion}
Overall, we did not find any general fooling technique that can be considered in new AI detectors, but we discovered that the detector, both for the image and text generated content, highly depends on the used generator. Therefore a specific processor might reduce the detection rate for some detectors while it increases the detection rate for others. Our pipeline consisting of creation, process and detection is simple, but effective, and can be used in further research.
